On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-11-07 paper.tex
Some more items from the "to do" list

Figure~\ref{fig: probmax_len} shows the probability $\probmax(\len)$ of visiting the maximum number of tiles on a unit square grid, as given by \eqref{eq: probmax}. As $\len$ grows, $\probmax(\len)$ has a jump when the maximum number of tiles that can be visited increases by $1$. This happens when $\len$ equals the right endpoint of the interval \eqref{eq: square, odd max tiles, lengths} for $\tiles$ odd or of \eqref{eq: square, even max tiles, lengths} for $\tiles$ even. Let these length values be denoted as $\len_\tiles$:
\begin{equation}
\len_\tiles = \begin{cases}
\displaystyle
\frac{\sqrt{(\tiles-3)^2 + (\tiles-1)^2}} {2} & \text{ for $\tiles$ odd, $\tiles \geq 3$} \\
\displaystyle
\frac{\tiles-2}{\sqrt{2}} & \text{ for $\tiles$ odd, $\tiles \geq 4$}.
\end{cases}
\end{equation}
For example, the first continuous section seen in Figure~\ref{fig: probmax_len} corresponds to a maximum number of tiles $\tiles=3$, for lengths in the interval $(0, \len_3]$, with $\len_3= 1$. The second corresponds to $\tiles=4$, for lengths in $(\len_3, \len_4]$, with $\len_4= \sqrt{2}$. Within each continuous section the probability monotonically increases from $0$ to a maximum value. The heights of the maxima follow a different trend**better word?** for odd and even $\tiles$, as can be seen in the figure; but in each case they are asymptotically proportional to $1/\len_\tiles$. This is established by the next result.

@@

@@

For \eqref{eq: probmax lim odd} it suffices to note that
\begin{align}
\label{eq: tedious limit, odd 1}
\lim_{\tiles \rightarrow \infty}\, \tiles g\left(\frac{\sqrt{(\tiles-3)^2+(\tiles-1)^2}} 2, \tiles-3, \tiles-3 \right) &= \frac 2 {3\pi} \\
\label{eq: tedious limit, odd 2}
\lim_{\tiles \rightarrow \infty}\, \tiles g\left(\frac{\sqrt{(\tiles-3)^2+(\tiles-1)^2}} 2, \tiles-5, \tiles-1 \right)
& = \frac 2 {3\pi},
\end{align}
as can be checked using L'H\^opital's rule \cite[section~5.3]{Abbott15}.
%***I think. It's very tedious by hand. I used Maple to compute the limit, and then checked it numerically. Maybe one or two intermediate steps from applying L'H\^opital's rule should be included. Perhaps those can be obtained with Maple too, and this part can be rewritten.
Combining these expressions with the second equality in \eqref{eq: probmax} yields \eqref{eq: probmax lim odd}.

>>>>

@@

Figure~\ref{fig: probmax_len} shows the probability $\probmax(\len)$ of visiting the maximum number of tiles on a unit square grid, as given by \eqref{eq: probmax}. As $\len$ grows, $\probmax(\len)$ has a jump when the maximum number of tiles that can be visited increases by $1$ (and there the function takes the value approached from the left). This happens when $\len$ equals the right endpoint of the interval \eqref{eq: square, odd max tiles, lengths} for $\tiles$ odd or of \eqref{eq: square, even max tiles, lengths} for $\tiles$ even. Let these length values be denoted as $\len_\tiles$:
\begin{equation}
\len_\tiles = \begin{cases}
\displaystyle
\frac{\sqrt{(\tiles-3)^2 + (\tiles-1)^2}} {2} & \text{ for $\tiles$ odd, $\tiles \geq 3$} \\
\displaystyle
\frac{\tiles-2}{\sqrt{2}} & \text{ for $\tiles$ odd, $\tiles \geq 4$}.
\end{cases}
\end{equation}
For example, the first continuous section seen in Figure~\ref{fig: probmax_len} corresponds to a maximum number of tiles $\tiles=3$, for lengths in the interval $(0, \len_3]$, where $\len_3= 1$. The second corresponds to $\tiles=4$, for lengths in $(\len_3, \len_4]$, where $\len_4= \sqrt{2}$. Within each continuous section the probability monotonically increases from $0$ to a maximum value. The heights of the maxima follow different trends for odd and even $\tiles$ respectively, as can be seen in the figure; but in each case they are asymptotically proportional to $1/\len_\tiles$. This is established by the next result.

@@

For \eqref{eq: probmax lim odd} it suffices to note that
\begin{align}
\label{eq: tedious limit, odd 1}
\lim_{\tiles \rightarrow \infty}\, \tiles g\left(\frac{\sqrt{(\tiles-3)^2+(\tiles-1)^2}} 2, \tiles-3, \tiles-3 \right) &= \frac 2 {3\pi} \\
\label{eq: tedious limit, odd 2}
\lim_{\tiles \rightarrow \infty}\, \tiles g\left(\frac{\sqrt{(\tiles-3)^2+(\tiles-1)^2}} 2, \tiles-5, \tiles-1 \right)
& = \frac 2 {3\pi},
\end{align}
as can be (somewhat tediously) checked using L'H\^opital's rule \cite[section~5.3]{Abbott15}.
%***I think. It's very tedious by hand. I used Maple to compute the limit, and then checked it numerically. Maybe one or two intermediate steps from applying L'H\^opital's rule should be included. Perhaps those can be obtained with Maple too, and this part can be rewritten.
Combining these expressions with the second equality in \eqref{eq: probmax} yields \eqref{eq: probmax lim odd}.
